Making multiple-locus association mapping on a genome-wide scale routine

### 2017-10-25 AM+draft.tex
26Oct2017 Working on methods - comparison methods

>>>>

\subsection{Comparison Methods}
Overview - 
  * Eagle compared to six other association mapping methods.  
  * 4 of these methods are multiple-locus methods
  * 2 of these methods are single-locus methods. 
  * methods were chosen because they were specifically designed for association mapping and have been implemented in computer
    software. 
  * Core features summarized in Table X. 
  * For each method, a summary of its underlying statistical theory is presented below.

Multiple locus methods

\subsubsection{BigRR}
BigRR is an R package that implements generalised ridge regression for
the analysis of genetic data (ref). Generalised ridge regression is an
extension of
ridge regression. It is based on linear models and is a regularisation
method.  When applied to the analysis of snp data, unlike ridge
regression
that shrinks snp effects by a constant amount, generalised ridge
regression allows the amount of shrinkage to vary across snp.
The challenge though is how to turn the size estimates of the snp
Effects into measures of significance. Xxx suggest permutation but we
instead
rely on stability selection (described below).

  *  \cite{shen2013novel}

Single locus methods
